Are Older Bugs More Expensive to Fix that Newer Bugs?

### 2015-07-29 data.tex
files reorged into 'old' and 'img'
Updates from ShareLaTeX

\begin{figure*}[!t]
\begin{center}
\includegraphics[width=6in]{waterfall-v2.png}
\end{center}
\caption{Different approaches to software development:  waterfall and agile (bottom left).}
\label{fig:waterfall}
\end{figure*}

>>>>

\begin{figure}[!t]  
\begin{center}
\includegraphics[width=2.5in]{img/waterfall-v3.png}  
\end{center}
\caption{Phases of our data.
Abbreviations: \newline
{\em Before}= before development;\newline
{\em Reqts}	  = requirements;\newline
{\em HLD}	  = high-level design;\newline
{\em IntTest} = Integration testing (with code from others);\newline
{\em SysTest} = system test (e.g. load stress tests);\newline
{\em AcceptTest}  = acceptance testing (with users);\newline
{\em review}        = private activity;\newline
{\em inspect}        = group activity.}
\label{fig:waterfall}
\end{figure}

### 2015-07-29 phaseDelay.tex
Updates from ShareLaTeX

\conferenceinfo{ICSE}{'16 Austin, Texas}
\title{Does Phase Delay Dramatically Increase Cost to Fix?}
\numberofauthors{3}
\author{
%\alignauthor 
Tim Menzies \\
       \affaddr{Dept. of Computer Science}\\
       \affaddr{North Carolina State U, USA}\\
       \email{tim.menzies@gmail.com}
\and%alignauthor 
William Nichols,Forest Shull \\
        \affaddr{Software Engineering Institute}\\
        \affaddr{Carnegie Mellon U, USA}\\
        \email{\{wrn,fjshull\}@sei.cmu.edu} 
\and %\alignauthor 
Lucas Layman \\
       \affaddr{Fraunhofer CESE} \\
       \affaddr{College Park, USA}\\ 
       \email{llayman@fc-md.umd.edu}
} 
\maketitle
\begin{abstract}
Does
repair time increase dramatically
the longer an issue persists in a system?
Many industrial practitioners and academics this   to be true.
This   belief is used to justify 
major investments in  software development
 processes and methods.

This
paper reports on the largest study on phase delay yet published.
Based on a sample of 
171 software projects from around the world (2006 and 2014),
 we find that this belief is  
incorrect. Specifically: the    time  to resolve an
issue   does {\em not} increase
the longer the issue remains in the system.

@@

\vspace{1mm}
\noindent
{\bf Keywords:} software processes, economics, phase delay, cost to fix.

\section{Introduction}
In 2013-2014, 
eleven  million programmers~\cite{pettey14} and
half a trillion dollars~\cite{avram14} was spent on information technology.
Such a large and growing effort should be managed and optimized via  well-researched conclusions.

It is standard practice
in other fields such as medicine,
to continually revisit old conclusions~\cite{prasad13}.
Accordingly, this paper revisits
the {\em phase delay effect}
i.e.,  the rule of thumb stating that the time required to resolve an issue in a software project increases dramatically 
the longer it remains in the system. Basili \& Boehm comment that since the 1980s,  phase delay:
\begin{quote}
...has been a major driver in focusing
industrial software practice on thorough
requirements analysis and design,
on early verification and validation, and
on up-front prototyping and simulation
to avoid costly downstream fixes~\cite{boehm01}.
\end{quote}
Basili and Boehm are not alone in this assessment of the significance of the phase delay effect. Our surveys of industrial practitioners (shown in \S\ref{survey}) reveal the phase delay effect to be
one of the most strongly-held beliefs amongst commercial software engineers.
Previously~\cite{me08a}, we used phase delay to justify the software practice
of 
Independent Verification \& Validation (IVV):
\bi
\item
IVV has been criticized as
ineffective. IVV engineers are external reviewers, so may be unfamiliar with the project details.
Hence,    IVV   can find the same or fewer bugs
as  developers.
\item
On the other hand,   when the IVV team finds bugs earlier than the developers then, due to the phase delay effect, this provides overall cost savings to the project. 
\ei
Note that this argument critically depends on the assumption that   fixing later-phase issues is  significantly more expensive than fixing them earlier (as does the views of Boehm and Basili and all the industrial practitioners
we interviewed in \S\ref{survey}). Accordingly, in this paper, we investigate several hypotheses:
\bi
    \item $H_1$: The cost to resolve issues dramatically increases across phases.
    \item $H_2$: The cost to resolve issues dramatically increases as the phase delay increases.
\ei
As we explored the above, we found a related hypothesis was believed by both professional software engineers and some academics:
\bi
 \item $H_3$: Requirements errors are the most expensive to fix.
\ei
The rest of the paper investigates these  hypotheses. First, we conduct a survey of practitioners and researchers to gauge their belief in the phase delay effect. Second, we  analyze 171 software  projects developed in the period 2006 to 2014.

@@

\\
235&   57&  115&  177&Code&CodeReview &1.00 &  ******************  \\
228&   56&  113&  176&Code&CodeInspect &0.99 & ******************  \\
243&   59&  125&  206&Code&IntTest &1.08 &     *******************  \\
191&   46&   95&  173&Code&SysTest &0.82 & ******** \\
269&   66&  133&  206&Code&UnitTest &1.15 & ************  \\
130&   31&   65&  122&Code&AcceptTest &0.56 & ******  \\
 \end{tabular}
\end{center}
\caption{Distribution of fix times seen in SEI TSP data. Left hand side bars
show scale up on median values.}
\label{fig:raw}
\end{figure*}

>>>>

\conferenceinfo{ICSE}{'16 Austin, Texas}
\title{Are Older Bugs More Expensive to Fix that Newer Bugs? }
\numberofauthors{3}
\author{
%\alignauthor 
Tim Menzies \\
       \affaddr{Computer Science}\\
       \affaddr{NC State University, USA}\\
       \email{tim.menzies@gmail.com}
\and%alignauthor 
William Nichols, Forest Shull \\
        \affaddr{Software Engineering Institute}\\
        \affaddr{Carnegie Mellon U, USA}\\
        \email{\{wrn,fjshull\}@sei.cmu.edu} 
\and %\alignauthor 
Lucas Layman \\
       \affaddr{Fraunhofer CESE} \\
       \affaddr{College Park, USA}\\ 
       \email{llayman@fc-md.umd.edu}
} 
\maketitle
\begin{abstract}
Does
repair time increase dramatically
the longer an issue persists in a system?
Many industrial practitioners and academics this   to be true.
This   belief is used to justify 
major investments in  software development
 processes and methods.

This
paper reports on the largest study on phase delay yet published.
Based on a sample of 
171 software projects from around the world (2006 and 2014),
 we find that this belief is  
incorrect. Specifically: the    time  to resolve an
issue   does {\em not} increase
the longer that issue remains in the system.

@@

\vspace{1mm}
\noindent
{\bf Keywords:} software economics, phase delay, cost to fix.

\section{todo}

four hypotheses: time = cost;
intra project PD;
post project PD;
intra predicts for post

comment on why post is no longer current. continuous deployment. package managers.Windows moving from service patches (which occur rarely) to continuous deployment (so there will be no windows 11... just a stream of continuous updates).   architectural incubators: big superstructures within which it is simpler and cheaper to do many small projects. e.g. aircraft carriers,  packet-stitching. mean stack (to be clear: none of the data explored in this paper comes from such architectural incubators: this paragraph is only meant to be a  speculation of future implications of this old data to newer projects).

\section{Introduction}
In 2013-2014, 
eleven  million programmers~\cite{pettey14} and
half a trillion dollars~\cite{avram14} were spent on information technology.
Such a large and growing effort should be managed and optimized via  well-researched conclusions.

It is standard practice
in other fields such as medicine,
to continually revisit old conclusions~\cite{prasad13}.
Accordingly, this paper revisits
the {\em phase delay effect}
i.e.,  the rule of thumb stating that the time required to resolve an issue in a software project increases dramatically 
the longer it remains in the system. Basili \& Boehm comment that since the 1980s,  phase delay
``...has been a major driver in focusing
industrial software practice on thorough
requirements analysis and design,
on early verification and validation, and
on up-front prototyping and simulation
to avoid costly downstream fixes''~\cite{boehm01}.

Basili and Boehm are not alone in this assessment of the significance of the phase delay effect.
For example,
our surveys of industrial practitioners (shown in \S\ref{survey}) reveal the phase delay effect to be
one of the most strongly-held beliefs amongst commercial software engineers.
Also,  previously~\cite{me08a} we used phase delay to justify the software practice
of 
Independent Verification \& Validation (IVV). Specifically,  when the IVV team finds bugs earlier than the developers then (due to the phase delay effect) this provides overall cost savings to the project. 
Note that this argument critically depends on the assumption that fixing later-phase issues is  significantly more expensive than fixing them earlier (as does the views of Boehm and Basili and all the industrial practitioners
we interviewed in \S\ref{survey}).

Accordingly, in this paper, we investigate several hypotheses related to this widely-held belief:
\bi
    \item $H_1$: The cost to resolve issues dramatically increases across phases.
    \item $H_2$: The cost to resolve issues dramatically increases as the phase delay increases.
\ei
As we explored the above, we found a related hypothesis was believed by both professional software engineers and some academics:
\bi
 \item $H_3$: Requirements errors are the most expensive to fix.
\ei
The rest of the paper investigates these  hypotheses. First, we conduct a survey of practitioners and researchers to gauge their belief in the phase delay effect. Second, we  analyze 171 software  projects developed in the period 2006 to 2014.

@@

\\
235&   57&  115&  177&Code&CodeReview &1.00 &  **********  \\
228&   56&  113&  176&Code&CodeInspect &0.99 & ********** \\
243&   59&  125&  206&Code&IntTest &1.08 &     *********** \\
191&   46&   95&  173&Code&SysTest &0.82 &     ******** \\
269&   66&  133&  206&Code&UnitTest &1.15 &    ***********  \\
130&   31&   65&  122&Code&AcceptTest &0.56 &  ******  \\
 \end{tabular}
\end{center}
\caption{Distribution of fix times seen in SEI TSP data. Left hand side bars
show scale up on median values.}
\label{fig:raw}
\end{figure*}
